---
title: "code_challenge_bella"
format: html
editor: source
---
Note:
*aoi_bps_models <- bps_aoi_atts$BPS_MODEL #subset ref_con to aoi aoi_ref_con <- subset(ref_con, Model_Code %in% aoi_bps_models)*

# Code Challenge:

##1. Load Data Into Environment
>practice chart

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)

ggplot(scls_aoi_attributes, aes(x=REL_PERCENT, y=LABEL)) + 
  geom_bar(stat = "identity")
```

##2. Merge datasets
```{r}
merged_names <- left_join(bps_model_number_name, ref_con_modified, by = "Model_Code")

colnames(scls_aoi_attributes)[colnames(scls_aoi_attributes) == "VALUE"] <- "Var2"

merged_variance <- merge(combine_raw, scls_aoi_attributes, by = "Var2")

colnames(merged_names)[colnames(merged_names) == "Model_Code"] <- "BPS_MODEL"

merged_names2 <- merge(merged_names, LF16_BPS_200, by = "BPS_MODEL")
```

> I had a mess of data in my environment after this, by creating the correct data through trial and error. I wish I had been more intentional in my naming because it made things more difficult leaving them with their original names, I would have to keep looking through the datasets to remember what I needed from them. 

#practice charts:
```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)

ggplot(merged_variance, aes(x=REL_PERCENT, y=LABEL)) + 
  geom_bar(stat = "identity")

ggplot(merged_names, aes(x=BPS_MODEL, y= A)) +
  geom_bar(stat= "identity")

```

##3. Filter
```{r}
filtered_df2 <- filter(merged_names, BPS_MODEL == "13040_32_43_44_49" | BPS_MODEL == "15070_44" | BPS_MODEL == "13670_32_44")

```

> This didn't work initially and I am not sure why... only filtered 1 name rather than all 3. Didn't merge correctly.

>Tried to merge with LF16 but had the same issue

> Ended up filtering by model code and that worked, didn't need to merge LF16 ?

##4. Mutate? 
*(Get percents)
*(Get past vs present)
